shrimp_goby_boatnoise

### 2024-10-22 ms_boatnoise_shrimp_goby.Rmd
removing comment
Changed a lot of the figures and cleaned up the directory storage so that certain folders can be ignored

#1. Data wrangling
##1.1 Loading the required packages
```{r, message=FALSE, results='hide'}
#install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, brms, cmdstanr, broom, broom.mixed, tidybayes, ggthemes, emmeans, ggdist, gridExtra, bayesplot, see, patchwork, ggtext, extraDistr)

@@

shrimp_species <- read.csv("./2-data/species.csv")

length(unique(BORIS_output$code))

@@

#filtering for the behviours of interest to this experiment
workingdf2 <- workingdf1 |> 
  group_by(unique_id) |> 
  filter(behaviour == 'INSIDE' | behaviour == 'EDGE' | behaviour == 'NEAR' | behaviour == 'AWAY' |behaviour == 'CONTACT' |behaviour == 'APART' ) |>
  mutate(averageduration = sum(duration))

#becuase of the way BORIS outputs data there are redundant individuals in the data, e.g., even if there are only two shrimp in a burrow then BORIS will still output observations for a third shrimp and all value will be 0's. this is what this section of code is removing
workingdf3 <- workingdf2 |> 
  group_by(burrow, species, individual) |> 
  filter(sum(averageduration) != 0)
```

###1.4.3 Assigning values to missing entries
```{r}
#now here we are making the assumption that when a goby or shrimp is present in other videos but missing from the video of focus it is either away and out of frame for the entire trial if it is a goby. Otherwise it is inside the burrow the entire time if it is a shrimp. These assumptions are based off of preliminary observation and the general tendencies of each species. Because of this assumption we are assigning the respective value to the behviour in cases where one of the species is known to be present in a burrow but not viewed for the length of the trial. 
fixeddf1 <- workingdf3 |> 
  filter(averageduration == 0) |> 
  mutate(duration = ifelse(species == "Goby" & behaviour == "AWAY", 300, duration),
         duration = ifelse(species == "Shrimp" & behaviour == "INSIDE", 300, duration)
         )

fixeddf2 <- workingdf3 |> 
  filter(averageduration != 0)

@@

#now using the number of conspecifics to calculate a duration value that represents the mean time spent doing that activity for that species (i.e. goby or shrimp) in that burrow as we are un able to preserve identity and thus instead must look at species averages for each behaviour. 
workingdf5 <- workingdf4 |> 
  group_by(burrow_species, behaviour, stage) |> 
  dplyr::mutate(mean_duration = mean(duration)) |> 
  ungroup() |> 
  filter(individual == 1)

@@

goby_df <- workingdf7 |> 
  filter(species == "Goby") |> 
  rename(goby_out = away, goby_total = total, goby_number = number_conspecifics) |> 
  select(-c("inside", "species", "burrow_species", "burrow_species_stage", "shrimp_contact"))

shrimp_df <- workingdf7 |> 
  filter(species == "Shrimp") |> 
  rename(shrimp_out = away, shrimp_total = total, shrimp_number = number_conspecifics) |> 
  select(c("shrimp_out", "shrimp_total", "shrimp_number", "burrow_stage", "shrimp_contact"))

@@

write_csv(final_df, "final_df.csv")
```

@@

# Extract the relevant contrast information
goby_out_results.table <- as.data.frame(goby_out_contrast_effect) |> 
  filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))

@@

goby_out_temporal_contrasts <- goby_out_contrast_draws |> 
  filter(contrast %in% c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post")) |> 
  mutate(stroke = ifelse(contrast %in% c("control Pre - control During", "control Pre - control Post"), "Control", ifelse(contrast %in% c("4 Pre - 4 During", "4 Pre - 4 Post"), "4", "2")))

@@

fig.goby_out_temporal_contrasts
```
###2.3.3 Plot of raw data and predicted estimates
####2.3.3.1 Extracting model estimates
```{r}
goby_out_model_estimates <- goby_out_model |> 
  emmeans(~ stroke*stage,
          epred = TRUE,
          rg.limit = 14000,
          re_formula = NA)

@@

write.csv(goby_out_model_estimates, "goby_out_model_estimates.csv")

goby_out_model_estimates_control <- goby_out_model_estimates |> 
  filter(stroke == "control") |> 
  rename(.value = emmean)

goby_out_model_estimates_four <- goby_out_model_estimates |> 
  filter(stroke == "4")|> 
  rename(.value = emmean)

goby_out_model_estimates_two <- goby_out_model_estimates |> 
  filter(stroke == "2")|> 
  rename(.value = emmean)
```

####2.3.3.2 Plotting control estimates and raw data
```{r}
goby_control_raw_data <- final_df |> 
  filter(stroke =="control") |> 
  rename(.value = goby_out)

goby_control_raw_data$stage <- factor(goby_control_raw_data$stage, levels = c("Post", "During", "Pre"))

#assigning a value for the baseline mean
goby_out_model_estimates_control_intercept <- goby_out_model_estimates_control %>%
  filter(stage == "Pre") %>%
  pull(.value)

goby_out_fig_control <- ggplot(goby_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_violin(alpha = 0.7, size = 0) +
  geom_hline(yintercept = goby_out_model_estimates_control_intercept, linetype = "dashed")+
  geom_jitter(width = 0.1) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_control, size = 2, position = position_nudge(x = 0.5)) +
  labs(x="Period relative to treatment") +
  theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.title.y = element_text(size = 13, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_line(colour = "#ededed"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("Control")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c")) +
  coord_flip()

goby_out_fig_control
```
####2.3.3.3 Plotting 4-stroke estimates and raw data
```{r}
goby_four_raw_data <- final_df |> 
  filter(stroke =="4") |> 
  rename(.value = goby_out)

goby_four_raw_data$stage <- factor(goby_four_raw_data$stage, levels = c("Post", "During", "Pre"))

#assigning a value for the baseline mean
goby_out_model_estimates_four_intercept <- goby_out_model_estimates_four %>%
  filter(stage == "Pre") %>%
  pull(.value)

goby_out_fig_four <- ggplot(goby_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_violin(alpha = 0.7, size = 0) +
  geom_hline(yintercept = goby_out_model_estimates_four_intercept, linetype = "dashed")+
  geom_jitter(width = 0.1) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_four, size = 2, position = position_nudge(x = 0.5)) +
  ylab("Proportion of time spent out of the burrow")+
  theme(legend.position = "none", 
        axis.title.y = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.x = element_text(size = 13, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_line(colour = "#ededed"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("4-stroke")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b")) +
  coord_flip()

@@

####2.3.3.4 Plotting 2-stroke estimates and raw data
```{r}
goby_two_raw_data <- final_df |> 
  filter(stroke =="2") |> 
  rename(.value = goby_out)

goby_two_raw_data$stage <- factor(goby_two_raw_data$stage, levels = c("Post", "During", "Pre"))

goby_out_model_estimates_two_intercept <- goby_out_model_estimates_two %>%
  filter(stage == "Pre") %>%
  pull(.value)

goby_out_fig_two <- ggplot(goby_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_violin(alpha = 0.7, size = 0) +
  geom_hline(yintercept = goby_out_model_estimates_two_intercept, linetype = "dashed")+
  geom_jitter(width = 0.1) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.5))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_two, size = 2, position = position_nudge(x = 0.5)) +
  theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        plot.title = element_textbox_simple(face = "bold", size = 14, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_line(colour = "#ededed"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("2-stroke")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a")) +
  coord_flip()

goby_out_fig_two
```
####2.3.3.5 Combining plots into one window
```{r}
# Combine the plots
goby_out_plot <- goby_out_fig_control + goby_out_fig_four + goby_out_fig_two + 
  plot_layout(ncol = 3)

# Display the combined plot
goby_out_plot

ggsave("goby_out_plot.png", plot = goby_out_plot, units = "px", width = 1500, height = 800, dpi = 320, scale = 2)
```

###2.3.4 Modelling the effect of covariates on the proportion of time gobies spent outside of the burrow
####2.3.4.1 Goby number
```{r}
goby_out_goby_number <- goby_out_model |>
  emmeans(~ goby_number, 
          epred = TRUE,
          re_formla = NULL) |> 
  contrast(method = "revpairwise")

@@

# Extract the relevant contrast information
shrimp_out_contrasts <- as.data.frame(shrimp_out_contrasts) |> 
  filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))

@@

shrimp_out_temporal_contrasts <- shrimp_out_contrast_draws |> 
  filter(contrast %in% c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post")) |> 
  mutate(stroke = ifelse(contrast %in% c("control Pre - control During", "control Pre - control Post"), "Control", ifelse(contrast %in% c("4 Pre - 4 During", "4 Pre - 4 Post"), "4", "2")))

@@

shrimp_out_temporal_contrasts_fig
```
###2.4.3 Plot of raw data and predicted estimates
####2.4.3.1 Extracting model estimates
```{r}
shrimp_out_model_estimates <- shrimp_out_model |> 
  emmeans(~ stroke*stage,
          epred = TRUE,
          rg.limit = 14000,
          re_formula = NA)

@@

write.csv(shrimp_out_model_estimates, "shrimp_out_model_estimates.csv")

shrimp_out_model_estimates_control <- shrimp_out_model_estimates |> 
  filter(stroke == "control") |> 
  rename(.value = emmean)

shrimp_out_model_estimates_four <- shrimp_out_model_estimates |> 
  filter(stroke == "4")|> 
  rename(.value = emmean)

shrimp_out_model_estimates_two <- shrimp_out_model_estimates |> 
  filter(stroke == "2")|> 
  rename(.value = emmean)
```

####2.4.3.2 Plotting control estimates and raw data
```{r}
shrimp_control_raw_data <- final_df |> 
  filter(stroke =="control") |> 
  rename(.value = shrimp_out)

shrimp_control_raw_data$stage <- factor(shrimp_control_raw_data$stage, levels = c("Post", "During", "Pre"))

#assigning a value for the baseline mean
shrimp_out_model_estimates_control_intercept <- shrimp_out_model_estimates_control %>%
  filter(stage == "Pre") %>%
  pull(.value)

>>>>

#1. Data wrangling
##1.1 Loading the required packages
```{r, message=FALSE, results='hide'}
#install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, brms, cmdstanr, broom, broom.mixed, tidybayes, ggthemes, emmeans, ggdist, gridExtra, bayesplot, see, patchwork, ggtext, extraDistr, gghalves, ggpp, rstan)

@@

#reading in shrimp species information
shrimp_species <- read.csv("./2-data/species.csv")

@@

#filtering for the behviours of interest to this experiment
workingdf2 <- workingdf1 |> 
  group_by(unique_id) |> 
  dplyr::filter(behaviour == 'INSIDE' | behaviour == 'EDGE' | behaviour == 'NEAR' | behaviour == 'AWAY' |behaviour == 'CONTACT' |behaviour == 'APART' ) |>
  mutate(averageduration = sum(duration))

#becuase of the way BORIS outputs data there are redundant individuals in the data, e.g., even if there are only two shrimp in a burrow then BORIS will still output observations for a third shrimp and all value will be 0's. this is what this section of code is removing
workingdf3 <- workingdf2 |> 
  group_by(burrow, species, individual) |> 
  dplyr::filter(sum(averageduration) != 0)
```

###1.4.3 Assigning values to missing entries
```{r}
#now here we are making the assumption that when a goby or shrimp is present in other videos but missing from the video of focus it is either away and out of frame for the entire trial if it is a goby. Otherwise it is inside the burrow the entire time if it is a shrimp. These assumptions are based off of preliminary observation and the general tendencies of each species. Because of this assumption we are assigning the respective value to the behviour in cases where one of the species is known to be present in a burrow but not viewed for the length of the trial. 
fixeddf1 <- workingdf3 |> 
  dplyr::filter(averageduration == 0) |> 
  mutate(duration = ifelse(species == "Goby" & behaviour == "AWAY", 300, duration),
         duration = ifelse(species == "Shrimp" & behaviour == "INSIDE", 300, duration)
         )

fixeddf2 <- workingdf3 |> 
  dplyr::filter(averageduration != 0)

@@

#now using the number of conspecifics to calculate a duration value that represents the mean time spent doing that activity for that species (i.e. goby or shrimp) in that burrow as we are un able to preserve identity and thus instead must look at species averages for each behaviour. 
workingdf5 <- workingdf4 |> 
  group_by(burrow_species, behaviour, stage) |> 
  dplyr::mutate(mean_duration = mean(duration)) |> 
  ungroup() |> 
  dplyr::filter(individual == 1)

@@

goby_df <- workingdf7 |> 
  dplyr::filter(species == "Goby") |> 
  rename(goby_out = away, goby_total = total, goby_number = number_conspecifics) |> 
  select(-c("inside", "species", "burrow_species", "burrow_species_stage", "shrimp_contact"))

shrimp_df <- workingdf7 |> 
  dplyr::filter(species == "Shrimp") |> 
  rename(shrimp_out = away, shrimp_total = total, shrimp_number = number_conspecifics) |> 
  select(c("shrimp_out", "shrimp_total", "shrimp_number", "burrow_stage", "shrimp_contact"))

@@

write_csv(final_df, "./2-data/final_df.csv")
```

@@

# Extract the relevant contrast information
goby_out_results.table <- as.data.frame(goby_out_contrast_effect) |> 
  dplyr::filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))

@@

goby_out_temporal_contrasts <- goby_out_contrast_draws |> 
  dplyr::filter(contrast %in% c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post")) |> 
  mutate(stroke = ifelse(contrast %in% c("control Pre - control During", "control Pre - control Post"), "Control", ifelse(contrast %in% c("4 Pre - 4 During", "4 Pre - 4 Post"), "4", "2")))

@@

fig.goby_out_temporal_contrasts
```
###2.3.3 Extracting and plotting model estimates
####2.3.3.1 Extracting estimates
```{r}
goby_out_model_estimates <- goby_out_model |> 
  emmeans(~ stroke*stage,
          epred = TRUE,
          rg.limit = 14000,
          re_formula = NA)

@@

write.csv(goby_out_model_estimates, "./2-data/goby_out_model_estimates.csv")

#Storing the model estimate means for each group to plot later on
goby_out_model_estimates_control <- goby_out_model_estimates |> 
  dplyr::filter(stroke == "control") |> 
  rename(.value = emmean)

goby_out_model_estimates_four <- goby_out_model_estimates |> 
  dplyr::filter(stroke == "4")|> 
  rename(.value = emmean)

goby_out_model_estimates_two <- goby_out_model_estimates |> 
  dplyr::filter(stroke == "2")|> 
  rename(.value = emmean)
```
####2.3.3.2 Plotting model estimates and raw data
```{r}
goby_out_model_draws <- goby_out_model |> 
  emmeans(~ stroke*stage,
          epred = TRUE,
          rg.limit = 14000,
          re_formula = NA) |> 
  gather_emmeans_draws()

goby_out_model_draws <- goby_out_model_draws |> 
  rename(emmean = .value)

goby_out_raw_data <- final_df |> 
  rename(emmean = goby_out)

goby_out_raw_data$stage <- factor(goby_out_raw_data$stage, levels = c("Pre", "During", "Post"))
goby_out_raw_data$stroke <- factor(goby_out_raw_data$stroke, levels = c("control", "4", "2"))

goby_out_model_estimates$stage <- factor(goby_out_model_estimates$stage, levels = c("Pre", "During", "Post"))
goby_out_model_estimates$stroke <- factor(goby_out_model_estimates$stroke, levels = c("control", "4", "2"))

goby_out_model_draws$stage <- factor(goby_out_model_draws$stage, levels = c("Pre", "During", "Post"))
goby_out_model_draws$stroke <- factor(goby_out_model_draws$stroke, levels = c("control", "4", "2"))

goby_out_means <- goby_out_raw_data |> 
  group_by(stage, stroke) |> 
  summarise(emmean = mean(emmean))

goby_out_fig_together <- ggplot(data = goby_out_raw_data, aes(x = stage, y = emmean, color = stroke, fill = stroke)) +
  geom_point(data = goby_out_means, alpha = 1, position = position_dodgenudge(width = 0.8, x = -0.09), size = 9, shape = "_") +
  geom_half_point(alpha = 0.3, position = position_dodgenudge(width = 0.8, x = -0.03), side = "l", range_scale = 0.5) +
  geom_half_violin(data = goby_out_model_draws, aes(x = stage, y = emmean, color = stroke, fill = stroke), alpha = 0.6, position = position_dodge(width = 0.8), side = "r", size = 0) +
  geom_point(data = goby_out_model_estimates, aes(x = stage, y = emmean, color = stroke), position = position_dodge(width = 0.8), size = 3) +
  geom_errorbar(data = goby_out_model_estimates, aes(x = stage, y = emmean, ymin = lower.HPD, ymax = upper.HPD, color = stroke), position = position_dodge(width = 0.8), width = 0, size = 1.25) +
  scale_fill_manual(values = c("control" = "#76A34A", "4" = "#F29E00", "2" = "#E25A00"), name = "Noise exposure", guide = guide_legend(override.aes = list(size = 3))) +
  scale_color_manual(values = c("control" = "#2A330E", "4" = "#805213", "2" = "#542709"), name = "Noise exposure", guide = guide_legend(override.aes = list(size = 3))) +
  scale_x_discrete(labels = c("Pre", "During", "Post")) +
  labs(title = "The effects of boat noise on goby burrow use",
       y = "Proportion of time in out of the burrow",
       x = "Experimental phase relative to noise exposure") +
  theme_classic() +
  theme(
    axis.text.x = element_text(size = 10, margin = margin(t = 5)),  
    axis.text.y = element_text(size = 10, margin = margin(r = 5)),  
    axis.title.x = element_text(size = 13, margin = margin(t = 10)),
    axis.title.y = element_text(size = 13, margin = margin(r = 10)),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 10),
    legend.position = "right",
    legend.justification = "top",
    plot.title = element_text(hjust = 0.5, size = 16),  
    plot.margin = margin(10, 10, 10, 10)
  )

goby_out_fig_together
ggsave("./3-figs/goby_out_fig_together.png", plot = goby_out_fig_together, units = "px", width = 2200, height = 1400, dpi = 300)
```

####2.3.3.3 Plotting control estimates and raw data
```{r}
goby_out_model_draws <- goby_out_model |> 
  emmeans(~ stroke*stage,
          epred = TRUE,
          rg.limit = 14000,
          re_formula = NA) |> 
  gather_emmeans_draws()

goby_out_raw_data <- final_df |>
  rename(.value = goby_out)

goby_out_model_draws$stage <- factor(goby_out_model_draws$stage, levels = c("Pre", "During", "Post"))
goby_out_model_draws$stroke <- factor(goby_out_model_draws$stroke, levels = c("control", "4", "2"))

goby_out_control_model_draws <- goby_out_model_draws |> 
  dplyr::filter(stroke == "control")

goby_control_raw_data <- final_df |> 
  dplyr::filter(stroke =="control") |> 
  rename(.value = goby_out)

goby_control_means <- goby_control_raw_data |> 
  group_by(stage) |> 
  summarise(.value = mean(.value))

goby_control_raw_data$stage <- factor(goby_control_raw_data$stage, levels = c("Pre", "During", "Post"))

#assigning a value for the baseline mean
goby_out_model_estimates_control_intercept <- goby_out_model_estimates_control %>%
  dplyr::filter(stage == "Pre") %>%
  pull(.value)

goby_out_fig_control <- ggplot(goby_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = goby_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = goby_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  labs(x="Period relative to treatment",
       y="Proportion of time out of burrow") +
  theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.text.x = element_text(size = 13),  
        axis.text.y = element_text(size = 13),
        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("Control")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c"))

goby_out_fig_control
```
####2.3.3.4 Plotting 4-stroke estimates and raw data
```{r}
goby_out_control_model_draws <- goby_out_model_draws |> 
  dplyr::filter(stroke == "4")

goby_four_raw_data <- final_df |> 
  dplyr::filter(stroke =="4") |> 
  rename(.value = goby_out)

goby_four_raw_data$stage <- factor(goby_four_raw_data$stage, levels = c("Pre", "During", "Post"))

goby_four_means <- goby_four_raw_data |> 
  group_by(stage) |> 
  summarise(.value = mean(.value))

goby_out_fig_four <- ggplot(goby_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = goby_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = goby_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  xlab("Experimental phase relative to noise exposure")+
  theme(legend.position = "none", 
        axis.title.y = element_blank(),  
        axis.text.x = element_text(size = 13),  
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("4-stroke")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))

@@

####2.3.3.5 Plotting 2-stroke estimates and raw data
```{r}
goby_out_control_model_draws <- goby_out_model_draws |> 
  dplyr::filter(stroke == "2")

goby_two_raw_data <- final_df |> 
  dplyr::filter(stroke =="2") |> 
  rename(.value = goby_out)

goby_two_raw_data$stage <- factor(goby_two_raw_data$stage, levels = c("Pre", "During", "Post"))

goby_two_means <- goby_two_raw_data |> 
  group_by(stage) |> 
  summarise(.value = mean(.value))

goby_out_fig_two <- ggplot(goby_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = goby_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = goby_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  theme(legend.position = "none", 
        axis.title.x = element_blank(),  
        axis.text.x = element_text(size = 13),
        axis.title.y = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("2-stroke") +
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))

goby_out_fig_two
```
####2.3.3.6 Combining plots into one figure
```{r}
goby_out_plot3 <- goby_out_fig_control + goby_out_fig_four + goby_out_fig_two + 
  plot_layout(ncol = 3)

goby_out_plot3
ggsave("./3-figs/goby_out_plot3.png", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
```

###2.3.4 Effects of covariates on the proportion of time gobies spent outside of the burrow
####2.3.4.1 Goby number
```{r}
goby_out_goby_number <- goby_out_model |>
  emmeans(~ goby_number, 
          epred = TRUE,
          re_formla = NULL) |> 
  contrast(method = "revpairwise")

@@

# Extract the relevant contrast information
shrimp_out_contrasts <- as.data.frame(shrimp_out_contrasts) |> 
  dplyr::filter(contrast %in% c("control Pre - 2 Pre", "control Pre - 4 Pre","4 Pre - 2 Pre", "control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post"))

@@

shrimp_out_temporal_contrasts <- shrimp_out_contrast_draws |> 
  dplyr::filter(contrast %in% c("control Pre - control During", "control Pre - control Post", "4 Pre - 4 During", "4 Pre - 4 Post", "2 Pre - 2 During", "2 Pre - 2 Post")) |> 
  mutate(stroke = ifelse(contrast %in% c("control Pre - control During", "control Pre - control Post"), "Control", ifelse(contrast %in% c("4 Pre - 4 During", "4 Pre - 4 Post"), "4", "2")))

@@

shrimp_out_temporal_contrasts_fig
```

###2.4.3 Extracting and plotting model estimates
####2.4.3.1 Extracting estimates
```{r}
shrimp_out_model_estimates <- shrimp_out_model |> 
  emmeans(~ stroke*stage,
          epred = TRUE,
          rg.limit = 14000,
          re_formula = NA)

@@

write.csv(shrimp_out_model_estimates, "./2-data/shrimp_out_model_estimates.csv")

#Storing the model estimate means for each group to plot later on
shrimp_out_model_estimates_control <- shrimp_out_model_estimates |> 
  dplyr::filter(stroke == "control") |> 
  rename(.value = emmean)

shrimp_out_model_estimates_four <- shrimp_out_model_estimates |> 
  dplyr::filter(stroke == "4")|> 
  rename(.value = emmean)

shrimp_out_model_estimates_two <- shrimp_out_model_estimates |> 
  dplyr::filter(stroke == "2")|> 
  rename(.value = emmean)
```
####2.4.3.2 Plotting model estimates and raw data
```{r}
shrimp_out_model_draws <- shrimp_out_model |> 
  emmeans(~ stroke*stage,
          epred = TRUE,
          rg.limit = 14000,
          re_formula = NA) |> 
  gather_emmeans_draws()

shrimp_out_model_draws <- shrimp_out_model_draws |> 
  rename(emmean = .value)

shrimp_out_raw_data <- final_df |> 
  rename(emmean = shrimp_out)

shrimp_out_raw_data$stage <- factor(shrimp_out_raw_data$stage, levels = c("Pre", "During", "Post"))
shrimp_out_raw_data$stroke <- factor(shrimp_out_raw_data$stroke, levels = c("control", "4", "2"))

shrimp_out_model_estimates$stage <- factor(shrimp_out_model_estimates$stage, levels = c("Pre", "During", "Post"))
shrimp_out_model_estimates$stroke <- factor(shrimp_out_model_estimates$stroke, levels = c("control", "4", "2"))

shrimp_out_model_draws$stage <- factor(shrimp_out_model_draws$stage, levels = c("Pre", "During", "Post"))
shrimp_out_model_draws$stroke <- factor(shrimp_out_model_draws$stroke, levels = c("control", "4", "2"))

shrimp_out_means <- shrimp_out_raw_data |> 
  group_by(stage, stroke) |> 
  summarise(emmean = mean(emmean))
